\documentclass[12pt, letterpaper]{article}
\begin{document}
First document. This is a simple example, with no 
extra parameters or packages included.

This is how you make text \textbf{bold}

This is how you make text \underline{underlined} 

This is how you do \textit{italics}


\noindent \textbf{Describe your career goals and how this program would help you fulfill them}
\\\\
\noindent The NREIP program aligns very well with my career goals 
which has two major comopnents. One bing finding places to work at and people to work with 
who share a desire to work in meaningful STEM research. The second component being having a desire to work 
with others people who share a passion of being a lifelong learners. My passion lies in conducting impactful 
research that addresses real-world challenges. Through NREIP, I would have the opportunity to engage in 
meaningful STEM research projects directly related to Naval science and technology. This hands-on experience 
would not only strengthen my research skills but also allow me to contribute to the advancement of critical 
technologies. Fulfilling my career goals requires exposure to such research opportunities, 
which NREIP provides abundantly. Additionally, I feel that NREIP provides an exccelent opportunity for me to 
be exposed to others who try to life as lifelong learners. I am committed to pursuing a STEM career, and my 
ultimate goal is to make meaningful contributions to the scientific community. Participating in NREIP w
ould not only enhance my education but also provide me with invaluable mentorship. Collaborating with 
laboratory scientists and engineers would allow me to deepen my understanding of STEM disciplines and 
broaden my horizons. This program wouldhelp me fulfill my career aspirations by providing a rich learning
environment.\\\\
\noindent \textbf{Advancing My STEM Education}
\\


\noindent I am committed to pursuing a STEM career, and my ultimate goal is to make meaningful contributions 
to the scientific community. Participating in NREIP would not only enhance my education but also 
provide me with invaluable mentorship. Collaborating with laboratory scientists and engineers would 
allow me to deepen my understanding of STEM disciplines and broaden my horizons. This program would
help me fulfill my career aspirations by providing a rich learning environment.

\noindent \textbf{Participation in Meaningful STEM Research:}
\\


My passion lies in conducting impactful research that addresses real-world challenges. Through NREIP,
I would have the opportunity to engage in meaningful STEM research projects directly related to
Naval science and technology. This hands-on experience would not only strengthen my research skills
but also allow me to contribute to the advancement of critical technologies. Fulfilling my career
goals requires exposure to such research opportunities, which NREIP provides abundantly.


\textbf{Describe any special interests you have that would make you a valuable participant}

answer here

\textbf{Describe any research experience you may have in relation to this program, including any STEM afterschool programs, camps, or competitions in which you have participated}

answer here

\textbf{Describe any technical skills you may have which are related to the science and engineering disciplines}

answer here

\textbf{Please use this section to share any information, not captured in any other sections, which you feel will be helpful to your application}

answer here
% \textbf{Describe any special interests you have that would make you a valuable participant}

% answer here
% % Describe your career goals and how this program would help you fulfill them․
%     - Find places to work that solve problems and solve hard problems. Working with novel technologies.
%     development of technology across TRL levels
%     -  Lifelong learning
%     - "I guess i'm just a researcher" 


% Describe any special interests you have that would make you a valuable participant․
    - 

% Describe any research experience you may have in relation to this program, including any 
% STEM afterschool programs, camps, or competitions in which you have participated․
    - 

% Describe any technical skills you may have which are related to the science and engineering disciplines․
    - 

% Please use this section to share any information, not captured in any other sections, which you feel 
% will be helpful to your application․

\end{document}